Exp. 2 Analysis: 2AFC, adults vs. children

### 2021-01-11 analysis/exp2_analysis.Rmd
CogSci skeleton to report online experiments

# make long
Nsubj_ch = length(unique(cd$ID))
# shown 1 object to drop, choose which target
ch_long <- cd %>%
  pivot_longer(cols = 4:23,
                   names_to = "drop",
                   values_to = "choice",
                   values_drop_na = FALSE) %>%
    mutate(drop = tolower(drop)) %>%
    mutate(drop = case_when(
      drop=="torus_1" ~ "torus",
      drop=="cone_1" ~ "cone",
      drop=="pyramid_1" ~ "pyramid",
      drop=="dumbbell_1" ~ "dumbbell",
      drop=="octahedron_1" ~ "octahedron",
      drop=="pipe_1" ~ "pipe",
      drop=="trig prism_1" ~ "trig prism",
      drop=="pentagon_1" ~ "pentagon",
      drop=="sphere_1" ~ "sphere",
      drop=="bowl_1" ~ "bowl",
      TRUE ~ drop
    )) %>% mutate(Trial = rep(1:20, Nsubj_ch)) %>% 
  mutate(
    target = rep(c("pipe", "cone", "cone", "pyramid", "pipe", "bowl", "bowl", "bowl", "torus", "torus",
               "bowl", "pentagon", "trig prism", "torus", "pentagon", "pipe", "trig prism", "pentagon", "pipe", "torus"), Nsubj_ch), # matches relation (containment/support)
    relation = rep(c(rep("contain", 10), rep("support", 10)), Nsubj_ch) #c(rep(, 10), rep( , 10))
  ) %>% 
  mutate(chose_target = ifelse(choice == target, 1, 0))

child_trial_agg <- ch_long %>% group_by(relation, drop, target) %>% # alt, 
  summarize(chose_target=mean(chose_target, na.rm=T), n=n())

@@

```{r}
table(ch_long$drop, ch_long$choice)
```

@@

combo_dat <- ch_long %>% mutate(ID = as.character(ID),
                                Age = as.character(Age)) %>%
  select(ID, Age, Trial, choice, drop, target, relation, chose_target) %>%
  bind_rows(adult_long) %>% 
  mutate(AgeGroup = ifelse(Age!="adult", "child", "adult"))

>>>>

# make long
Nsubj_ch = length(unique(cd$ID))
# shown 1 object to drop, choose which target
child_long <- cd %>%
  pivot_longer(cols = 4:23,
                   names_to = "drop",
                   values_to = "choice",
                   values_drop_na = FALSE) %>%
    mutate(drop = tolower(drop)) %>%
    mutate(drop = case_when(
      drop=="torus_1" ~ "torus",
      drop=="cone_1" ~ "cone",
      drop=="pyramid_1" ~ "pyramid",
      drop=="dumbbell_1" ~ "dumbbell",
      drop=="octahedron_1" ~ "octahedron",
      drop=="pipe_1" ~ "pipe",
      drop=="trig prism_1" ~ "trig prism",
      drop=="pentagon_1" ~ "pentagon",
      drop=="sphere_1" ~ "sphere",
      drop=="bowl_1" ~ "bowl",
      TRUE ~ drop
    )) %>% mutate(Trial = rep(1:20, Nsubj_ch)) %>% 
  mutate(
    target = rep(c("pipe", "cone", "cone", "pyramid", "pipe", "bowl", "bowl", "bowl", "torus", "torus",
               "bowl", "pentagon", "trig prism", "torus", "pentagon", "pipe", "trig prism", "pentagon", "pipe", "torus"), Nsubj_ch), # matches relation (containment/support)
    relation = rep(c(rep("contain", 10), rep("support", 10)), Nsubj_ch) #c(rep(, 10), rep( , 10))
  ) %>% 
  mutate(chose_target = ifelse(choice == target, 1, 0))

save(adult_long, child_long, file=here("paper/processed_data.RData"))

child_trial_agg <- child_long %>% group_by(relation, drop, target) %>% # alt, 
  summarize(chose_target=mean(chose_target, na.rm=T), n=n())

@@

```{r}
table(child_long$drop, child_long$choice)
```

@@

combo_dat <- child_long %>% mutate(ID = as.character(ID),
                                Age = as.character(Age)) %>%
  select(ID, Age, Trial, choice, drop, target, relation, chose_target) %>%
  bind_rows(adult_long) %>% 
  mutate(AgeGroup = ifelse(Age!="adult", "child", "adult"))
